Joint Power Allocation and Network Slicing In an End to End O-RAN System

### 2019-10-03 Latex/tex/pr.tex
latex update 1

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\section{System Model and Problem Formulation}
In this section, first, we present the downlink (DL) of O-RAN System. Then we obtain achievable rate and delays.
Afterward, the main problem is expressed.
\subsection{System Model}
Suppose that there are $S$ Slices Serving $V$ Services. Each Service $v\in \{1,2,...,V \} $, consists of $U_v$ single antenna users that require certain service. Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $N_s$ PRBs. Each RRH $r \in \{1,2,...,R \}$ is connected to BBU pool via an optical fiber link with limited fronthaul capacity. Also each RRH and PRB can serve more than one slice. It is considered that in BBU, the system has 2 processing layer consists of $M_1$ homogeneous VMs in first layer and $M_2$ homogeneous VMs in second layer.
\subsection{Achievable Rate}
In this subsection, the Achievable Rate is obtained as below.
The achievable data rate for $i^{th}$ UE in $v^{th}$ service can be written as 
\begin{equation}
R_{u(v,i)} = B \log_2({1+ \rho_{u(v,i)}})
\end{equation}
where $\rho_{u(v,i)}$ is obtained from 
\begin{equation}
\rho_{u(v,i)} =  \frac{P_{u(v,i)}}{BN_0 + I_{u(v,i)}}
\end{equation}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\section{System Model and Problem Formulation}
In this section, first, we present the downlink (DL) of O-RAN System. Then we obtain achievable rate and delays.
Afterward, the main problem is expressed.
\subsection{System Model}
Suppose that there are $S$ Slices Serving $V$ Services. Each Service $v\in \{1,2,...,V \} $, consists of $U_v$ single antenna users that require certain service. Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $N_s$ PRBs. All the RRHs in a slice that is mapped to a service, transmit signals to all the UEs in specific service. Each RRH $r \in \{1,2,...,R \}$ is connected to BBU pool via an optical fiber link with limited fronthaul capacity. Also each RRH and PRB can serve more than one slice. It is considered that in BBU, the system has 2 processing layer consists of $M_1$ homogeneous VMs in first layer and $M_2$ homogeneous VMs in second layer.
\subsection{Achievable Rate}
In this subsection, the Achievable Rate is obtained as below.
The achievable data rate for $i^{th}$ UE in $v^{th}$ service can be written as 
\begin{equation}\label{eq1}
\mathcal{R}_{u(v,i)} = B \log_2({1+ \rho_{u(v,i)}})
\end{equation}
where $B$ is the bandwidth of system and $\rho_{u(v,i)}$ is the SNR of $i^{th}$ UE in $v^{th}$ service which is obtained from 
\begin{equation}\label{eq2}
\rho_{u(v,i)} =  \frac{P_{u(v,i)}\sum_{s=1}^{N_s}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{vs}}{BN_0 + I_{u(v,i)}}
\end{equation}
Where, $P_{u(v,i)}$ represents the transmitted power allocated by RRHs to $i^{th}$ UE in $v^{th}$ service. Also, 
$\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of wireless link from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service. In addition, $\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ depicts the the transmit beamforming vector from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service. Moreover, $BN_0$ denotes the power of guassian additive noise and $I_{u(v,i)}$ is the power of interfering signals. 
To obtain SNR as formulated in equation \eqref{eq2}, let $\bold{y}_{U_v}\in \mathbb{C}^{U_v} $ be the received signal's vector of all users in $v^{th}$ service which is given by equation \eqref{eq3}
\begin{equation}\label{eq3}
\bold{y}_{U_v} = \sum_{k=1}^{N_k}\sum_{s = 1}^{N_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{R}_s}+ \boldsymbol{q}_{R_s}) \zeta_{U_v,k}+ \boldsymbol{z}_{\mathcal{U}_v}
\end{equation}
where $\boldsymbol{x}_{ \mathcal{R}_s} = [x_{ r_{(s,1)}},...,x_{ r_{(s,\mathcal{R}_s)}}]^T \in \mathbb{C}^{{R}_s } $ depicts the transmitted symbol vector for the $s$-th set of Network slice,  $\boldsymbol{z}_{U_v}$ is the additive Gaussian noise $\boldsymbol{z_{U_v}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{{U}_v})$ and $N_0$ is the noise power.
In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise which is made from signal compression in BBU.
\\
Furthermore, $\zeta_{U_v,k} \delequal \{\zeta_{u(v,1),k},\zeta_{u(v,2),k},...,\zeta_{u(v,N_{U_v}),k}\}$,
$\zeta_{u(v,i),k} \in \{0,1\}$ is a binary parameter that map Physical Resource Blocks(PRB) to UE.
Also as defined before, $\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}=\left[\boldsymbol{h}_{\mathcal{R}_s,u_{(v,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_s,v_{(v,\mathcal{U}_v)}}\right]^T  \in \mathbb{C}^{{R}_s\times {U}_v }$ 
shows the channel matrix between RRH set $\mathcal{R}_s$ to UE set
$\mathcal{U}_v$. 
The channel vector from the RRH of  $s^{th}$ slice to the $i^{th}$ UE in the $v^{th}$ service $\boldsymbol{h}_{\mathcal{R}_s,u_{(v,i)}}\in \mathbb{C}^{{R}_s}$ is modeled as below
\begin{equation}
\boldsymbol{h}_{\mathcal{R}_s,u_{(s,i)}} = \boldsymbol{\beta}^\frac{1}{2}_{\mathcal{R}_s,u_{(v,i)}} \boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}},
\end{equation}
where $\boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{\mathcal{U}_v})$ indicates the fast fading and flat fading channel vector and $\boldsymbol{\beta}_{\mathcal{R}_s,u_{(v,i)}}=\text{diag}(a_{r_{(s,1),u_{(v,i)}}},\ldots,a_{r_{(s,\mathcal{R}_s),u_{(v,i)}}})$
represents the large scale fading matrix.
\\
Moreover, $\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = [\boldsymbol{w}_{\mathcal{R}_s,u(v,1)},...,\boldsymbol{w}_{\mathcal{R}_s,u(v,U_v)}] \in \mathbb{C}^{{R}_s\times U_v} $ is the zero forcing beamforming vector to minimize the interference which is indicated as follow
\begin{equation}
\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}^H \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v})^{-1}
\end{equation}
Hence, the interference power of $i^{th}$ UE in $v^{th}$ service can be represented as follow
\begin{equation}
\begin{split}
 I_{u_{(v,i)}} &= 
 \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{u_{(v,l)}}a_{vs}\zeta_{u_(v,i),n}\zeta_{u_(v,l),n}}_{\text{(intra-service interference)}}\\
&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}a_{ys} \zeta_{u_(v,i),n}\zeta_{u_(y,l),n}}_{\text{(inter-service interference)}}\\
&+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{{R}_s} {\sigma_q}_{r_{(s,j)}}^2 |\boldsymbol{h}_{r_{(s,j)}, u_{(v,i)}}|^2 a_{vs}}_{\text{(quantization noise interference)}}.
\end{split}
\end{equation}
where, $\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(v,l)}}|^2$
and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$.
let $\bar{p}_{r_{(s,j)}}$ denote the power of transmitted signal from $j^{th}$ RRH in $s^{th}$ slice.
from equation \eqref{eq3} we have
\begin{equation}
\bar{p}_{r_{(s,j)}} = \sum_{v=1}^{V}\boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   \boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}}^H a_{vs} + \sigma_{q_{r(s,j)}}^2.
\end{equation}
As a result the user data capacity on the fronthual link between BBU and the $j^{th}$ RRH in $s^{th}$ slice is formulated as below
\begin{equation}
C_{R_{(s,j)}} = \log{(1+\sum_{v=1}^{V}\frac{w_{r_{(s,j)},\mathcal{D}_{s}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   w_{r_{(s,j)},\mathcal{U}_{v}}^H a_{vs}}{ \sigma_{q_{r(s,j)}}^2})},
\end{equation}
It is assumed that we have two processing layer in BBU of O-RAN system. as we mentioned before, we have $M_1$ VMs in the first layer and $M_2$ VMs in second layer. Each VM in both layers map to one or more slices. So in $s^{th}$ slice, there are $M_{s_1}$ VMs in first layer and $M_{s_2}$ VMs in second layer. Each VM in first and second layer has computational capacity that is  equal to $\mu_1$ and $\mu_2$ respectively. 
